%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Introduction 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \section{Introduction}
% \label{contents}


\section{What is “machine learning”?}

human: learning (why do human need to learn, and what is purpose of learning, and how to learning)
Learning is the process of acquiring new understanding, knowledge, behaviors, skills, values, attitudes, and preferences.[1]
https://en.wikipedia.org/wiki/Learning

A machine can predict new samples using summarized (“learned”) experience from historical data

1. Why do we need a machine (smart agent, robot) can learn?
a. Use machine with “knowledge” like human to save people’s time from heavy or repeat workload (rescue people from heavy workload by machine)
b. Find some latent “rule” or pattern from big data that peope can’t found, don’t find, or easy ignore, and use them to make decision or predict for future data
c. Some dangerous work, human Cann’t or don’t want to do
d…

\subsection{Is “learning” possible for a machine? (Is a machine can learn?)}
1. IF so, under what conditions?
something that is PAC-learnable
(the hypothesis space H is finite
the hypothesis space iH s infinite)
In this framework, the learner receives samples and must select a generalization function (called the hypothesis) from a certain class of possible functions. The goal is that, with high probability (the "probably" part), the selected function will have low generalization error (the "approximately correct" part). The learner must be able to learn the concept given any arbitrary approximation ratio, probability of success, or distribution of the samples.

\section{Why can we learning from data?}

\section{How to learn?}
1. How does a machine learn?
2. How to learn from data?
different machine learning algorithm

How the learning is good?
How to learning fast?
What is the best results we can learn?

\section{Is the learn from data is meaningful and useful? (Generalization)    }
1. Is the learned model from data is a good model?
2. How to evaluate the learned results (learned model)?
3. How to use generalization error to guide training phase?

\section{What’s difference between human learning and machine learning?}
7. Can a machine beat human?
1. Some aspect they can (data process)
2. Some aspect they Cann’t (concionous analysis)

\section{Can we become a teacher to a machine? Or vice verse?}

\section{How to make learning more efficient? (Learn fast, i.e., converge fast)}

\section{How to make learning more intelligent? (i.e., smaller test error)}

\section{Can a machine grow up with time? (Iterative learning or life-long learner)}


\section{Direction?}

need to design efficient and accurate algorithms, analysis of complexity, theoretical guarantees.


